---
title: 'Data Science - Homework #1'
author: "Jon Brock - JPB2210"
output: 
    github_document:
    toc: TRUE
    toc_float: TRUE
---

```{r load_packages, include = FALSE}
library(tidyverse)
```

## Problem #1
##### *Create a data frame with specific inclusions:*

```{r create_data_frame}
prob1_df <- tibble(
    vec_numeric = rnorm(8),
    vec_logical = vec_numeric > 0,
    vec_character = c("beat", "cream", "fold", "glaze", "knead", "score", "whip", "whisk"),
    vec_factor = c("good", "neutral", "bad", "good", "neutral", "bad", "good", "bad")
)
```
***

##### *Taking the mean value of each vector within our data frame:*

The mean value of `vec_numeric` is `r mean(pull(prob1_df, vec_numeric))`.  
The mean value of `vec_logical` is `r mean(pull(prob1_df, vec_logical))`.  
The mean value of `vec_character` is `r mean(pull(prob1_df, vec_character))`.  
The mean value of `vec_factor` is `r mean(pull(prob1_df, vec_factor))`.  

We see that we are unable to take the mean value from `vec_character` and `vec_factor`. Additionally, while we did take a mean value from `vec_logical` it's merely a mean of 0's and 1's.

```{r vector_conversions, eval = FALSE}
#THIS SECTION IS PENDING COMPLETION.
```
***