---
title: 'Data Science - Homework #1'
author: "Jon Brock - JPB2210"
output: 
    github_document:
    toc: TRUE
    toc_float: TRUE
---

```{r load_packages, include = FALSE}
library(tidyverse)
```

## Problem #1
##### *Create a data frame with specific inclusions:*

```{r create_data_frame_1}
prob1_df <- tibble(
    vec_numeric = rnorm(8),
    vec_logical = vec_numeric > 0,
    vec_character = c("beat", "cream", "fold", "glaze", "knead", "score", "whip", "whisk"),
    vec_factor = c("good", "neutral", "bad", "good", "neutral", "bad", "good", "bad")
)
```
***

##### *Taking the mean value of each vector within our data frame:*

The mean value of `vec_numeric` is `r mean(pull(prob1_df, vec_numeric))`.  
The mean value of `vec_logical` is `r mean(pull(prob1_df, vec_logical))`.  
The mean value of `vec_character` is `r mean(pull(prob1_df, vec_character))`.  
The mean value of `vec_factor` is `r mean(pull(prob1_df, vec_factor))`.  

We see that we are unable to take the mean value from `vec_character` and `vec_factor`. Additionally, while we did take a mean value from `vec_logical` it's merely a mean of 0's and 1's.

```{r vector_conversions, eval = FALSE}
#THIS SECTION IS PENDING COMPLETION
```
***

## Problem #2
##### *Create a data frame with specific inclusions:*

```{r create_data_frame_2}
prob2_df <- tibble(
    x = rnorm(500),
    y = rnorm(500),
    vec_logical_p2 = x + y > 1,
    vec_numeric_p2 = as.numeric(vec_logical_p2),
    vec_factor_p2 = as.factor(vec_logical_p2)
)
```
Let me tell you a few fun facts about my Problem #2 data frame:  
    1. The data frame **prob2_df** has **`r nrow(prob2_df)`** rows and **`r ncol(prob2_df)`** columns.














